### 2023-02-02 definitions.tex
details

\textcolor{red}{Thinking about whether or not it is pertinent to have LTS and not only TS. LTS can be usefull for TA because of the use of the guards/time as labels but it may be unecessary.}

@@

\textcolor{red}{This makes sense for TS but not so much for LTS ...}

@@

\textcolor{blue}{Alain: the forward coverability algorithm for infinitely branching TSs.; the backward cov algo may work for essentially finitely branching TSs.}
\textcolor{red}{Not sure that TS induced by TA are finitely branching. Actually I believe they are not, i.e. for instance for a TA with one clock $x$, from a state $q$ and clock $x$ set at $0$, if there is a transition e.g. $(q, x \geq 3, \emptyset, q')$ then the set of successors of 
$(q,0)$ is $\{q'\} \times \{3, 4, 5, \ldots \}$. Need to check where finitely branching appears as an assumption/requirement.}

>>>>

%\textcolor{red}{Thinking about whether or not it is pertinent to have LTS and not only TS. LTS can be usefull for TA because of the use of the guards/time as labels but it may be unecessary.}

@@

%\textcolor{red}{This makes sense for TS but not so much for LTS ...}

@@

%\textcolor{blue}{Alain: the forward coverability algorithm for infinitely branching TSs.; the backward cov algo may work for essentially finitely branching TSs.}
%\textcolor{red}{Not sure that TS induced by TA are finitely branching. Actually I believe they are not, i.e. for instance for a TA with one clock $x$, from a state $q$ and clock $x$ set at $0$, if there is a transition e.g. $(q, x \geq 3, \emptyset, q')$ then the set of successors of 
%$(q,0)$ is $\{q'\} \times \{3, 4, 5, \ldots \}$. Need to check where finitely branching appears as an assumption/requirement.}
